A Java Framework For Embarrassingly Parallel Problems

### 2013-12-12 paper/paper.tex
MORE PAPER

Figure \ref{fig:speedup} shows the speedup of the Ka/Ks Calculator program. 
In most of the samples, the speedup seems to level off between 6 to 10 workers,
and even goes down when increased to 16 workers. Running the framework at 50\% 
of the CPU is more efficient than running using 100\% of the CPU in this 
situation. The decrease in speedup from 8 workers to 16 workers shows that TODO.
This is not true of all case, as seen in sample E. This sample has a higher
speedup at 16 workers because the piece of work that comes Xth in the sample
takes the longest. With 16 workers, this chunk is started immediately instead of
most of the way through the total runtime of the framework.
\subsection{Octupus}

@@

It is clear that the framework provides an effective yet simple to use module to
add parallelism to a specific class of file-oriented embarrassingly parallel
problems. Two sentences with specifics from the graphs. More self-praise TODO

>>>>

Figure \ref{fig:speedup} shows the speedup of the Ka/Ks Calculator program. 
In most of the samples, the speedup seems to level off between 6 to 10 workers,
and even goes down when increased to 16 workers. Running the framework at 50\% 
of the CPU is more efficient than running using 100\% of the CPU in this 
situation. The decrease in speedup from 8 workers to 16 workers shows this.
This is not true of all case, as seen in sample E. This sample has a higher
speedup at 16 workers because there are multiple piece of work toward the end
that take a majority of the runtime. With 16 workers, these chunks were started
immediately instead of late during the total runtime of the framework.

\subsection{Octupus}

@@

It is clear that the framework provides an effective yet simple to use module to
add parallelism to a specific class of file-oriented embarrassingly parallel
problems. Speedup of 4x can be achieved on simple samples with the same number
of chunks as workers, and possibly slightly higher with real data, as seen with
the octupus data. While many consumer-level computers will not have many options
when it comes to chosing the proccesing power, the framework will help
universities and companies who have the raw computing power, and are just not
using it to their full potential.
